---
title: "Alcohol vs Seat choice"
author: "Briana Barba"
date: "Summer 2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

Based on the boxplot, the back row consumes more acohol than the front and middle rows.

## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=davisdata)
```

The mean for the people sitting in the back seats is three times higher than the people in the middle seats and increasingly higher for the people in the front seats.

## Inferential Tests
Since the p value from one way annova was such 
```{r}
model1 <- aov(alcohol~Seat,data=davisdata)
summary.aov(model1)
```

Since the p value from one way annova was such a smaller number we are going to follow up with tukeyhsd.

```{r}
plot(TukeyHSD(model1))
```

The middle-back and front-back confidence intervals are less than zero than the results would be significantly different. 

## Conclusions

Based on all data provided, the people within the back row drank the most alcohol. Most people were sat in the middle row being about two times more than the front and back rows. 
